---
title: "Deployment: Model-agnostic methods: Partial Dependency Plot (PDP)."
author: "Andrea Rodrigo"
output: html_document
---

```{r}
#Libraries
library(dplyr)
library(plotly)
library(reshape2)
library(lubridate)
library(randomForestSRC)
library(ggplot2)
```


# 1.- One dimensional Partial Dependence Plot.

The partial dependence plot shows the marginal effect of a feature on the predicted outcome of a previously fit model. 

### EXERCISE:

**Apply PDP to the regression example of predicting bike rentals. Fit a random forest approximation for the prediction of bike rentals (*cnt*). Use the partial dependence plot to visualize the relationships the model learned. Use the slides shown in class as model. **

```{r}
days=read.csv("day.csv")

days$dteday <- as_date(days$dteday)
days_since <- select(days, workingday, holiday, temp, hum, windspeed, cnt)
days_since$days_since_2011 <- int_length(interval(ymd("2011-01-01"), days$dteday)) / (3600*24)
days_since$SUMMER <- ifelse(days$season == 3, 1, 0)
days_since$FALL <- ifelse(days$season == 4, 1, 0)
days_since$WINTER <- ifelse(days$season == 1, 1, 0)
days_since$MISTY <- ifelse(days$weathersit == 2, 1, 0)
days_since$RAIN <- ifelse(days$weathersit == 3 | days$weathersit == 4, 1, 0)
days_since$temp <- days_since$temp * 47 - 8
days_since$hum <- days_since$hum * 100
days_since$windspeed <- days_since$windspeed * 67

rf <- rfsrc(cnt~., data=days_since)
results <- select(days_since, days_since_2011, temp, hum, windspeed, cnt)
nr <- nrow(days_since)
for(c in names(results)[1:4])
{
  for(i in 1:nr){
    r <- days_since
    r[[c]] <- days_since[[c]][i]
    sal <- predict(rf, r)$predicted
    results[[c]][i] <- sum(sal) / nr
  }
}

p1 <- ggplot(days_since, aes(x=days_since_2011, y = results$days_since_2011)) + geom_line() + geom_rug(alpha=0.1, sides="b") + ylim(0, 6000) + xlab("Days since 2011") + ylab("Prediction")
p2 <- ggplot(days_since, aes(x=temp, y = results$temp)) + geom_line() + geom_rug(alpha=0.1, sides="b") + ylim(0, 6000) + xlab("Temperature") + ylab(NULL)
p3 <- ggplot(days_since, aes(x=hum , y = results$hum)) + geom_line() + geom_rug(alpha=0.1, sides="b") + ylim(0, 6000) + xlab("Humidity") + ylab(NULL)
p4 <- ggplot(days_since, aes(x=windspeed, y = results$windspeed)) + geom_line() + geom_rug(alpha=0.1, sides="b") + ylim(0, 6000) + xlab("Wind speed") + ylab(NULL)

subplot(p1,p2,p3,p4, shareY = T, titleY=T, titleX=T)


```


### QUESTION:

**Analyse the influence of *days since 2011, temperature, humidity* and *wind speed* on the predicted bike counts.**

  • *days_since_2011*: There is a positive correlation between the prediction    of rented bicycles and the number of days since 2011. However, there is not a   strong positive correlation, as the number of rented bicycles slightly         decreases at certain points. 
  
  • *temp*: The number of rented bicycles increases with temperature, but once   it surpasses 25 degrees, the opposite occurs, and it begins to decrease. This   makes sense, as typically, people do not feel like riding bicycles when it is   either too cold or too hot.
  
  • *windspeed*: If the wind speed is below 25, there is a negative correlation   because if there is too much wind, it is uncomfortable to ride a bicycle.We    cannot say much about wind speed above 25 because there are not enough         samples.
  
  • *hum*: We cannot say much about humidity below 50 because there are not      enough samples. However, if the humidity is above 50, there is a negative      correlation because as humidity increases, it becomes more uncomfortable to    ride a bicycle.
  
  

# 2.- Bidimensional Partial Dependency Plot.

### EXERCISE:

**Generate a 2D Partial Dependency Plot with humidity and temperature to predict the number of bikes rented depending on those parameters.**

***BE CAREFUL*: due to the size, extract a set of random samples from the BBDD before generating the data for the Partial Dependency Plot.**

**Show the density distribution of both input features with the 2D plot as shown in the class slides.**

***TIP*: Use geom_tile() to generate the 2D plot. Set width and height to avoid holes. **


### QUESTION:

**Interpret the results.**


# 3.- PDP to explain the price of a house.

### EXERCISE:

**Apply the previous concepts to predict the *price* of a house from the database *kc_house_data.csv*. In this case, use again a random forest approximation for the prediction based on the features *bedrooms, bathrooms, sqft_living, sqft_lot, floors* and *yr_built*. **

**Use the partial dependence plot to visualize the relationships the model learned.**

***BE CAREFUL*: due to the size, extract a set of random samples from the BBDD before generating the data for the Partial Dependency Plot.**


### QUESTION:

**Analyse the influence of bedrooms, bathrooms, sqft_living and floors on the predicted price.**



