---
title: "Deployment: Model-agnostic methods: Partial Dependency Plot (PDP)."
author: "Andrea Rodrigo"
output: html_document
---

```{r}
#Libraries

```


# 1.- One dimensional Partial Dependence Plot.

The partial dependence plot shows the marginal effect of a feature on the predicted outcome of a previously fit model. 

### EXERCISE:

**Apply PDP to the regression example of predicting bike rentals. Fit a random forest approximation for the prediction of bike rentals (*cnt*). Use the partial dependence plot to visualize the relationships the model learned. Use the slides shown in class as model. **

```{r}

```


### QUESTION:

**Analyse the influence of *days since 2011, temperature, humidity* and *wind speed* on the predicted bike counts.**


# 2.- Bidimensional Partial Dependency Plot.

### EXERCISE:

**Generate a 2D Partial Dependency Plot with humidity and temperature to predict the number of bikes rented depending on those parameters.**

***BE CAREFUL*: due to the size, extract a set of random samples from the BBDD before generating the data for the Partial Dependency Plot.**

**Show the density distribution of both input features with the 2D plot as shown in the class slides.**

***TIP*: Use geom_tile() to generate the 2D plot. Set width and height to avoid holes. **


### QUESTION:

**Interpret the results.**


# 3.- PDP to explain the price of a house.

### EXERCISE:

**Apply the previous concepts to predict the *price* of a house from the database *kc_house_data.csv*. In this case, use again a random forest approximation for the prediction based on the features *bedrooms, bathrooms, sqft_living, sqft_lot, floors* and *yr_built*. **

**Use the partial dependence plot to visualize the relationships the model learned.**

***BE CAREFUL*: due to the size, extract a set of random samples from the BBDD before generating the data for the Partial Dependency Plot.**


### QUESTION:

**Analyse the influence of bedrooms, bathrooms, sqft_living and floors on the predicted price.**



